An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex
Update main.tex

	\textit{\textbf{Single-Attribute Selectivity.}}
	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency.
%	, as the algorithm must efficiently identify data points matching specific attributes within large datasets. 
	AS is defined as the proportion of data points sharing a given attribute value. For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute. 
	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
%	We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
%	
%	Experimental results show that UNG achieves the best performance across all AS settings, especially at extremely low AS (1\%). 
%	This advantage stems from its pre-filtering strategy. Pre-filtering strategy significantly reduces the ANN search space by narrowing down candidates prior to vector computation. In contrast, VBASE performs the worst at 1\% AS due to its post-filtering strategy. Post-filtering strategy first retrieves a large number of candidates and then applies filtering, incurring substantial computational overhead.

@@

	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}. Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.

>>>>

	\textit{\textbf{Single-Attribute Selectivity.}}
	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency.
%	, as the algorithm must efficiently identify data points matching specific attributes within large datasets. 
	AS is defined as the proportion of data points sharing a given attribute value. For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute. 
	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset. 
%	We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
%	
%	Experimental results show that UNG achieves the best performance across all AS settings, especially at extremely low AS (1\%). 
%	This advantage stems from its pre-filtering strategy. Pre-filtering strategy significantly reduces the ANN search space by narrowing down candidates prior to vector computation. In contrast, VBASE performs the worst at 1\% AS due to its post-filtering strategy. Post-filtering strategy first retrieves a large number of candidates and then applies filtering, incurring substantial computational overhead.

@@

	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}. Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms}.
